---
title: "Advanced R by Hadley Wickham - Synthesis and experiments"
author: "Naren Srinivasan"
Version: 18.06.01
date: (`r format(Sys.Date(), "%B %d, %Y")`)
output:
  html_document:
    code_folding: show
    toc: yes
    toc_depth: 2
  html_notebook:
    toc: yes
    toc_depth: 2
  pdf_document:
    toc: yes
    toc_depth: '2'
---
```{r}
#library(devtools)
```
# Introduction

# 1 Names and Values
```{r Dependencies}
#devtools::install_github("r-lib/lobstr")
library(lobstr)
```

## 1.1 Binding basics

### 1.1.1 Synthesis

```{r Object address}
x <- 1:3
y <- x

lobstr::obj_addr(x)
lobstr::obj_addr(y)
```

* The name is a reference to value, as opposed to the value/object having a name
* When 'x' is assigned to 'y', it does not create another object, but rather, points to the same value
* The object points to a memory location/ address, and this changes every time you restart R. 


```{r Non-synctactic names}
# _abc <- 1

# The above line of code will throw an error. Try it out to see.

# Overriding R rules on names

`_abc` <- 1
str(`_abc`)
`_abc`
```

* The usual rules on names of R objects can be overrdide with backticks (`)
* This is useful in dealing with data coming from other systems, which have different rules than R

### 1.1.2 Exercises

#### Exercise 1

Explain the relationship between a, b, c and d in the following code:

```{r 1.1 Ex. 1 Q}
a <- 1:10
b <- a
c <- b
d <- 1:10
```

```{r 1.1 Ex. 1 A}
obj_addr(a)
obj_addr(b)
obj_addr(c)
obj_addr(d)
```
* A vector with values from 1 to 10 is defined as R object, with a memory address
* This is then mapped to the name 'a'
* The name 'b' is also mapped to the same address. So is 'c'
* Another vector with values from 1 to 10 is defined as *another* R object, and is mapped to the name 'd'
* This can be seen by inspecting the memory addresses of the objects. 'a', 'b', and 'c' should have the same address, while 'd' has a different one

#### Exercise 2

The following code accesses the mean function in multiple different ways. Do they all point to the same underlying function object? Verify with lobstr::obj_addr().

```{r 1.1 Ex. 2 Q}
mean
base::mean
get("mean")
evalq(mean)
match.fun("mean")
```


```{r 1.1. Ex.2 A}
obj_addr(mean)
obj_addr(base::mean)
obj_addr(get("mean"))
obj_addr(match.fun("mean"))
```

* Yes, in fact all these methods of accessing the 'mean' function refer to the same memory address. This can be verfied by noting that the memory addresses referred to in all these calls is the same

#### Exercise 3

By default, base R data import functions, like read.csv(), will automatically convert non-syntactic names to syntactic names. Why might this be problematic? What option allows you to suppress this behaviour?

```{r 1.1 Ex. 3 A}
?read.csv
```

* 
* The 'check.names' parameter allows the suppression of automatic conversion to synctactic names. Setting this to 'FALSE' disables automatic conversion

### Experiments











